Our Galactocentric Reference Frame Is Probably Wrong, and Not by a Little

### 2018-12-04 paper/ms.tex
Fix paper
Update paper

\newcommand{\Msun}{\text{M}_\odot}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}

@@

\newcommand{\mi}{\texttt{m12i}}
\newcommand{\mf}{\texttt{m12f}}
\newcommand{\mm}{\texttt{m12m}}

@@

\title{The Actions We Compute are Not Invariant}

@@

In an axisymmetric potential the 6D phase space of stars' positions and
velocities can be reduced to a 3D space of invariant actions. For this reason
actions are commonly used to help interpret phase space. We show that if one
assumes the wrong galactocentric reference frame this can induce artificial
non-axisymmetries which manifest as time dependence in the computed actions.
However, the Milky Way is not axisymmetric in detail and so there are no
truly axisymmetric axes. We instead define the  ``optimally axisymmetric''
axes as the reference frame which minimizes the time dependence of the
actions. Using cosmological zoom-in simulations from FIRE-2, we show that the
optimally axisymmetric reference frame can differ from standard methods of
calculating the galactocentric reference frame by (some numbers). We further
show that if one uses the conventional method to define the Galactic midplane
in this simulated galaxy, the midplane can vary by nearly a scale height
across the galaxy. This work calls into question the use of actions as
dynamical invariants unless these reference frame issues can be resolved.

@@

\section{Introduction} \label{sec:intro}

Midplane resolved with $\sim 370$ to $570$ star particles.

We could have proceeded by taking an axisymmetric potential and adding
analytic spiral arms, a bar, and gas clouds. However, in preliminary work
with the FIRE galaxies we found that defining a consistent reference frame
between snapshots was very difficult. An inaccuracy in the direction of the
$z$-axis by a single degree induces a $140\,\pc$ change in the height of the
midplane at $8.2\,\kpc$. In a cosmological context it is not apparent that
there exists a consistent definition of the galactocentric frame, and we
therefore proceed in a cosmological context to include this effect.

We perform a set of three different simulations repeated for two of the Milky
Way zoom-ins, \mi and \mf.\footnote{The number corresponds to the mass of the
dark matter halo (here, $\sim 10^{12} \Msun$). The first ``m'' stands for
mass and the last letter is a unique identifier for the {\em initial
conditions}.} The first assumes an axisymmetric potential and also implicitly
a well-defined galactocentric frame. This first simulation shows that our
integration technique respects the fact that in an axisymmetric potential
actions are invariant and that our calculation of the actions does not
imprint some artificial phase dependence in the actions.

\section{Methods} \label{sec:methods}
We begin by

Rockstar import in gizmo\_analysis is commented out

\subsection{Simulated Galaxies} \label{ssec:fire}
We wish to perform N-body integration within a realistic Galactic potential.
In order to do this, we use the {\em Latte} suite of Milky Way-mass zoom-ins
from the Feedback in Realistic Environments (FIRE)
collaboration\footnote{\url{http://fire.northwestern.edu}}
\citep{2016ApJ...827L..23W,2018MNRAS.480..800H}. In a zoom-in cosmological
simulation a high resolution region of interest is embedded within a low
resolution cosmological context (\Gus{cites}). In the case of {\em Latte}, a
region that will evolve into a Milky Way-mass galaxy, identified in a
preliminary dark matter only run, is increased in resolution using MUSIC.
This allows one to achieve ultra-high resolution simulations of individual
galaxies than possible in a full cosmological run.

Our centering differs from Sanderson et al. by $\sim3.2\,\pc$ for \mi.

\section{Optimally Axisymmetric Frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. We will perform a few simulations of small clusters in order to

@@

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $(\Omega_m, \Omega_{\Lambda}, \Omega_b, h, \sigma_8, n_s) =
(0.272, 0.728, 0.0455, 0.702, 0.807, 0.961)$, consistent with current
constraints \citep{2018arXiv180706209P}. Halos are selected at $z=0$ based
solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$). Particles
within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$ and the
initial conditions are regenerated at higher resolution using MUSIC
\citep{2011MNRAS.415.2101H}. A total of $\sim 10$ halos were simulated at
higher resolution \citep{2018MNRAS.481.4133G}.

These halos are uncontaminated and contain gas particles of mass $\sim 7000
\text{--} 20000 \Msun$ and star particles of mass $\sim 5000 \text{--} 7000
\Msun$, with the lower end coming from stellar evolution
\citep{2018arXiv180610564S}. Softening lengths for dark matter and star
particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions
(with cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and
$\abs{z}<1\,\kpc$) is $98\,\pc$.

@@

>>>>

\newcommand{\Msun}{\text{M}_\odot}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}
\newcommand{\kms}{\text{km}/\text{s}}

@@

\newcommand{\mi}{\texttt{m12i}}
\newcommand{\mf}{\texttt{m12f}}
\newcommand{\mm}{\texttt{m12m}}
\newcommand{\gdr}{{\em Gaia} DR2}

@@

\title{Our Galactocentric Reference Frame Is Probably Wrong, and Not by a
Little}

@@

In an axisymmetric potential the 6D phase space of stars' positions and
velocities can be reduced to a 3D space of invariant actions. We show that if
one assumes the wrong galactocentric reference frame this can induce
artificial non-axisymmetries which manifest as time dependence in the
computed actions. However, the Milky Way is not axisymmetric in detail and so
there are no truly axisymmetric axes. We instead define the  ``optimally
axisymmetric'' axes as the reference frame which minimizes the time
dependence of the computed actions. Standard methods for determining the
galactocentric reference frame typically involve finding the median height of
stars in the disk. Using cosmological zoom-in simulations from FIRE-2, we
show that the optimally axisymmetric reference frame can differ from standard
methods of calculating the galactocentric reference frame by nearly a scale
height. This work calls into question the use of actions as dynamical
invariants unless these reference frame issues can be resolved.

@@

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the era of \gdr. Recent major discoveries include the remnants of a major merger \citep{2018Natur.563...85H}, a phase-space spiral (\Gus{cites}) indicating local substructure infall (\Gus{cites}), a gap indicative of a dark matter subtructure in GD1 \citep{2018arXiv181103631B}, and \Gus{others}.

\section{Reference Frame Gone Wrong} \label{sec:ref_frame}
We begin by quantifying how

\section{Optimally Axisymmetric Frame} \label{sec:oa_frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. We will
perform a few simulations of small clusters embedded in the potential of a
frozen $\z=0$ snapshot of one such zoom-in. We take our fiducial reference
frame from \citet{2018arXiv180610564S}.

Freezing the potential means that during the course of our simulation the
cluster will rapidly pass by much of the substructure in the potential. To
illustrate that this has little effect on our results, we resimulate each
cluster with the softening lengths of the embedded potential increased by a
factor of \Gus{something}.

Once we perform this simulation, we calculate the actions of each star in the
cluster assuming the best-fit smooth, axisymmetric potential, as we do
observationally for the Milky Way. We refer to this space as the observational action space. We will find that there is significant time evolution in observational action space. Attributing some of this evolution to our fiducial reference frame being incorrect, we minimize the time-dispersion in action space

@@

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $\Omega_m = 0.272$, $\Omega_{\Lambda} = 0.728$, $\Omega_b =
0.0455$, $h = 0.702$, $\sigma_8 = 0.807$, and $n_s = 0.961$, consistent with
current constraints \citep{2018arXiv180706209P}. Halos are selected at $z=0$
based solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$).
Particles within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$
and the initial conditions are regenerated at higher resolution using MUSIC
\citep{2011MNRAS.415.2101H}. A total of $\sim 10$ halos were simulated at
higher resolution \citep{2018MNRAS.481.4133G}.

These halos are uncontaminated and contain gas particles of mass $\sim 7000
\text{--} 20,000\,\Msun$ and star particles of mass $\sim 5000 \text{--} 7000\,
\Msun$, with the lower end coming from stellar evolution
\citep{2018arXiv180610564S}. Softening lengths for dark matter and star
particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions
(with cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and
$\abs{z}<1\,\kpc$) is $98\,\pc$.

@@

Even though we change the center, we do not recalculate the center velocity.
This is largely irrelevant, as the recalculated center velocity differs from
the fiducial center velocity by $<0.1\,\kms$.
